# Data sources

## Data source links

The data is provided by NYC Department of Education and could be downloaded from NYC OpenData.

As shown in the FAQ document of NYC School Survey, the survey is voluntary and all District 75 students are provided with survey materials. All participants (parents, students, and teachers) involved are confidential, while only the teachers' responses are both anonymous and confidential. While the surveys may be completed online or by paper by parents and students, teachers are only allowed to take the survey online.

The result of parent, teacher and student response of the NYC school survey can be found in the links listed below:

https://data.cityofnewyork.us/Education/2019-NYC-School-Survey-Teachers/uzmq-2khh

https://data.cityofnewyork.us/Education/2019-NYC-School-Survey-Parents/4fcz-jias

https://data.cityofnewyork.us/Education/2019-NYC-School-Survey-Student/k2zg-756q

We download the dataset as `xlsx` format from the aforementioned websites.

## A glimpse at our dataset

### Dataframe on Aggregated Data

The survey contains a aggregated dataframe in which scores evaluating different dimensions of school performance are calculated based on students, teachers, and parents' responses.

#### Meanings of columns

Before we start to perform any exploratory data analysis and visualization, we need to understand what does each column mean in our dataset. The three dataframes we mentioned above -- Student, Teacher and Parent survey result -- contains 11 columns:

- DBN: Primary key for the dataset and identification of schools.

- School Name: School Name

- Total Parent/Teacher/Student Response Rate: Percentage rate of response from parent/teacher/student respectively, The response rate should be the same across datasets. 

- Collaborative Teachers Score

- Effective School Leadership Score

- Rigorous Instruction Score

- Supportive Environment Score

- Strong Family-Community Ties Score

- Trust Score 

Despite the aggregated dataframe should be exactly the same for all three datasets, it is different within each dataset The exact information on this dataframe from each dataset is displayed below. In summary, we concluded that the aggregated dataframe of teacher and parents' consists of DBNs where evaluation scores are completely void. Thus, we decide to look into the aggregated dataframe provided in the student response dataset.

#### Student Reponse dataset

The student response result is a dataframe with 1831 observations and 11 columns. As the first two rows of the dataframe is completely empty, the dataset actually consists of 1829 observations. Some important information are shown below: 

```{r}
library(readxl)
library(tidyverse)
student <- read_excel("Student.xlsx")
str(student)
```

#### Teacher Reponse dataset

Similarly, the teacher response result is a dataframe of 1,903 observations and 11 columns. Some important information are shown below:

```{r}
teacher <- read_excel("Teacher.xlsx")
str(teacher)
```

#### Parent Reponse dataset

The parent response result is a dataframe of 2,946 observations and 11 columns. Some important information are shown below:

```{r}
parents <- read_excel("Parent.xlsx")
str(parents)
```

### Data on Specific Question Responses
These dataframes shows the survey questions (all questions are multiple choice) and counts the number of responses that falls into each categories. Currently, each dataframe has questions as the column name, while the answer choices falls into the first row. Additionally, as each question may take up to five or six columns, there are hundreds of variables within each dataframe. Thus, after data cleaning, we have made choices to focus on some specific categories within each dataframes.

#### Student Reponse dataset

Student Reponse dataset is a dataframe of 1,111 observations and 272 columns. The actual observations should be 1109, as the first two rows are not comprised of statistics on survey response. Some examples of the dataset are shown below:

```{r}
qrstudent <- read_excel("Student.xlsx", 4)
head(qrstudent)
```

#### Teacher Reponse dataset

Student Reponse dataset is a dataframe of 1,905 observations and 579 columns. The actual observations should be 1903, as the first two rows are not comprised of statistics on survey response. Some examples of the dataset are shown below:

```{r}
qrteacher <- read_excel("Teacher.xlsx", 4)
head(qrteacher)
```

#### Parent Reponse dataset

Student Reponse dataset is a dataframe of 2948 observations and 196 columns. The actual observations should be 2946, as the first two rows are not comprised of statistics on survey response. Some examples of the dataset are shown below:

```{r}
qrparent <- read_excel("Parent.xlsx", 4)
head(qrparent)
```

## Issues with our data

As described earlier, our data primarily consists of two parts, the aggregated dataframe and dataframes on specific survey responses. While the survey responses are categorical, the aggregated dataframe consists of numerical values calculated based on these survey response. We did not obtain information on how these numerial values are calculated, thus our analysis is primarily based on the dataframes of specific survey responses. In order to conduct the analysis, we have cleaned and wrangled the dataframes on specific survey questions based on our own understanding.