# Data transformation
```{r}
library(readxl)
library(tidyverse)
agg <- read_excel("Student.xlsx")
student <- read_excel("Student.xlsx", 4)
teacher <- read_excel("Teacher.xlsx", 4)
parent <- read_excel("Parent.xlsx", 4)
```


## Step1: Change column names

The column names in the original dataset are too long and contain white spaces, which is inconvenient for future development. 

The column names of the aggregated datafrome after transformation is:

```{r}
agg <- agg %>%
  rename(student_rr = `Total Student Response Rate`) %>%
  rename(parent_rr = `Total Parent \r\nResponse Rate`) %>%
  rename(teacher_rr = `Total Teacher Response Rate`) %>%
  rename(name = `School Name`) %>%
  rename(trust = `Trust Score`) %>%
  rename(collab_teachers = `Collaborative Teachers Score`) %>%
  rename(effective_schlead = `Effective School Leadership Score`) %>%
  rename(rig_instruction = `Rigorous Instruction Score`) %>%
  rename(supp_env = `Supportive Environment Score`) %>%
  rename(family_communityties = `Strong Family-Community Ties Score`)
```

## Step 2: Transform survey response from student, teacher, and parents. 

The original dataframe contains survey questions as the column names. After loading the data in r, the answer choices is read as values in the first row. Thus, we have combined the answer choices within the column name for data wrangling and for the uniqueness of column names. Additionally, for the convenience of data wrangling, we have replaced the survey questions to question index in the column names.

Additionally, the data types of many columns are incorrect -- instead of character, they should be float. Therefore, we convert the data type of those columns to `numeric`.

```{r}
library(janitor)
# Student
student <- student %>%
  rename(student_rr = `Total Student Response Rate`) %>%
  rename(name = `School Name`)
s_colnames1 <- rep(c("1a", "1b", "1c", "1d", "1e", "1f", "1g", "1h", "1i", "1j", "1k"), each = 5)
s_colnames2 <- rep(c("2a", "2b", "2c", "2d", "2e", "3a", "3b", "3c", "3d", "3e", "4a", "4b", "4c", "4d", "4e", "4f", "4g", "4h", "4i", "5a", "5b", "5c", "5d", "5e", "6a", "6b", "6c", "6d", "6e", "6f", "6g", "6h", "6i", "7a", "7b", "7c", "7d", "8a", "8b", "8c", "8d", "8e", "8f", "8g", "8h", "9a", "9b", "10a", "10b", "10c", "10d"), each = 4)
s_colnames3 <-rep(c("11a", "11b"), each = 5)
s_colnames <- append(s_colnames1, s_colnames2)
s_colnames <- data.frame(append(s_colnames, s_colnames3))
colnames(s_colnames) <- "s_colnames"
s_ans1 <- data.frame(rep(c("s_disagree", "disagree", "agree", "s_agree", "idk"), times = 11))
colnames(s_ans1) <- "ans"
s_ans2 <- data.frame(rep(c("none", "few", "most", "all"), times = 10))
colnames(s_ans2) <- "ans"
s_ans3 <- data.frame(rep(c("s_disagree", "disagree", "agree", "s_agree"), times = 9))
colnames(s_ans3) <- "ans"
s_ans4 <- data.frame(rep(c("none", "few", "most", "all"), times = 14))
colnames(s_ans4) <- "ans"
s_ans5 <- data.frame(rep(c("s_disagree", "disagree", "agree", "s_agree"), times = 4))
colnames(s_ans5) <- "ans"
s_ans6 <- data.frame(rep(c("none", "rarely", "some", "most"), times = 8))
colnames(s_ans6) <- "ans"
s_ans7 <- data.frame(rep(c("s_disagree", "disagree", "agree", "s_agree"), times = 6))
colnames(s_ans7) <- "ans"
s_ans8 <- data.frame(rep(c("s_disagree", "disagree", "agree", "s_agree", "N/A"), times = 2))
colnames(s_ans8) <- "ans"
s_ans <- do.call("rbind", list(s_ans1, s_ans2, s_ans3, s_ans4, s_ans5, s_ans6, s_ans7, s_ans8))
s_colnames <- cbind(s_colnames, s_ans)
s_col <- paste0(s_colnames$s_colnames, "-", s_colnames$ans)
s <- c("DBN", "School Name", "student_rr")
s_col <- append(s, s_col)
colnames(student) <- s_col
student <- replace(student, student == "N/A", NA)
student <- student %>%
  slice(-c(1,2))
student[3:272] = as.data.frame(sapply(student[3:272], as.numeric))
```

A example of students' response after data wrangling:

```{r}
head(student)
```

```{r}
# Parent
parent <- parent %>%
  rename(parent_rr = `Total Parent Response Rate`) %>%
  rename(name = `School Name`)
p_colnames1 <- data.frame(rep(c("1a", "1b", "1c", "1d", "1e", "1f", "1g", "1h", "1i", "1j", "1k", "1l"), each = 4))
colnames(p_colnames1) <- "questions"
p_colnames2 <- data.frame(rep(c("2a", "2b", "2c", "2d", "2e", "2f", "2g", "2h", "3a", "3b", "3c"), each = 5))
colnames(p_colnames2) <- "questions"
p_colnames3 <- data.frame(rep(c("4a", "4b"), each = 4))
colnames(p_colnames3) <- "questions"
p_colnames4 <- data.frame(rep(c("5a", "5b", "5c", "5d", "5e"), each = 5))
colnames(p_colnames4) <- "questions"
p_colnames5 <- data.frame(rep(c("6a", "6b"), each = 4))
colnames(p_colnames5) <- "questions"
p_colnames6 <- data.frame(rep("7", each = 9))
colnames(p_colnames6) <- "questions"
p_colnames7 <- data.frame(rep(c("8a", "8b", "9a", "9b", "9c", "10a", "10b", "10c", "10d", "10e"), each = 4))
colnames(p_colnames7) <- "questions"
p_colnames <- do.call("rbind", list(p_colnames1, p_colnames2, p_colnames3, p_colnames4, p_colnames5, p_colnames6, p_colnames7))
p_ans1 <- data.frame(rep(c("s_disagree", "disagree", "agree", "s_agree"), times = 12))
colnames(p_ans1) <- "ans"
p_ans2 <- data.frame(rep(c("s_disagree", "disagree", "agree", "s_agree", "idk"), times = 11))
colnames(p_ans2) <- "ans"
p_ans3 <- data.frame(rep(c("never", "rarely", "sometimes", "often"), times = 2))
colnames(p_ans3) <- "ans"
p_ans4 <- data.frame(rep(c("v_dissatisfied", "dissatisfied", "satisfied", "v_satisfied", "idk"), times = 5))
colnames(p_ans4) <- "ans"
p_ans5 <- data.frame(rep(c("v_unlikely", "unlikely", "likely", "v_likely"), times = 2))
colnames(p_ans5) <- "ans"
p_ans6 <- data.frame(rep(c("leadership", "hands-on_learning", "enrichment_programs", "art_programs", "courses", "communication", "teaching", "class_size", "safety"), times = 1))
colnames(p_ans6) <- "ans"
p_ans7 <- data.frame(rep(c("s_disagree", "disagree", "agree", "s_agree"), times = 10))
colnames(p_ans7) <- "ans"
p_ans <- do.call("rbind", list(p_ans1, p_ans2, p_ans3, p_ans4, p_ans5, p_ans6, p_ans7))
p_colnames <- cbind(p_colnames, p_ans)
p_col <- paste0(p_colnames$questions, "-", p_colnames$ans)
p <- c("DBN", "School Name", "parent_rr")
p_col <- append(p, p_col)
colnames(parent) <- p_col
parent <- replace(parent, parent == "N/A", NA)
parent <- parent %>%
  slice(-c(1,2))
parent[3:196] = as.data.frame(sapply(parent[3:196], as.numeric))
```

A example of parents' response after data wrangling:

```{r}
head(parent)
```

```{r}
# Teacher
teacher <- teacher %>%
  rename(teacher_rr = `Total Teacher Response Rate`) %>%
  rename(name = `School Name`)
t_colnames1 <- data.frame(rep(c("1a", "1b", "1c", "1d", "1e"), each = 4))
colnames(t_colnames1) <- "questions"
t_colnames2 <- data.frame(rep(c("2a", "2b", "2c", "2d", "2e", "2f", "2g", "2h"), each = 5))
colnames(t_colnames2) <- "questions"
t_colnames3 <- data.frame(rep(c("3a", "3b", "3c", "3d", "3e", "4a", "4b", "4c", "4d", "4e", "4f", "4g", "4h", "5a", "5b", "5c", "5d", "5e", "5f", "5g", "5h", "5i", "6a", "6b", "6c", "6d", "6e", "6f", "6g", "6h", "7", "8", "9a", "9b", "9c", "9d", "9e", "9f", "10a", "10b", "10c", "10d", "10e", "11a", "11b", "11c", "11d", "12a", "12b", "12c", "12d", "12e", "13a", "13b", "13c", "13d", "13e", "14a", "14b", "14c", "14d", "14e"), each = 4))
colnames(t_colnames3) <- "questions"
t_colnames4 <- data.frame(rep(c("15a", "15b"), each = 5))
colnames(t_colnames4) <- "questions"
t_colnames5 <- data.frame(rep(c("16"), each = 7))
colnames(t_colnames5) <- "questions"
t_colnames6 <- data.frame(rep(c("17a", "17b", "18a", "18b", "18c", "18d", "19a", "19b", "19c"), each = 4))
colnames(t_colnames6) <- "questions"
t_colnames7 <- data.frame(rep(c("20a", "20b", "20c", "20d", "20e", "20f", "20g"), each = 5))
colnames(t_colnames7) <- "questions"
t_colnames8 <- data.frame(rep(c("21a", "21b", "21c", "21d", "21e", "22a", "22b", "22c", "22d", "22e", "22f", "22g", "22h", "22i"), each = 4))
colnames(t_colnames8) <- "questions"
t_colnames9 <- data.frame(rep(c("23a", "23b", "23c", "23d", "23e", "23f", "23g", "23h"), each = 5))
colnames(t_colnames9) <- "questions"
t_colnames10 <- data.frame(rep(c("24", "25a", "25b", "25c", "25d", "25e", "25f", "26a", "26b", "26c", "26d"), each = 4))
colnames(t_colnames10) <- "questions"
t_colnames11 <- data.frame(rep(c("27a", "27b", "28a", "28b", "28c", "28d", "28e", "28f"), each = 5))
colnames(t_colnames11) <- "questions"
t_colnames <- do.call("rbind", list(t_colnames1, t_colnames2, t_colnames3, t_colnames4, t_colnames5, t_colnames6, t_colnames7, t_colnames8, t_colnames9, t_colnames10, t_colnames11))
t_ans1 <- data.frame(rep(c("none", "some", "a_lot", "all"), times = 5))
colnames(t_ans1) <- "ans"
t_ans2 <- data.frame(rep(c("s_disagree", "disagree", "agree", "s_agree", "idk"), times = 8))
colnames(t_ans2) <- "ans"
t_ans3 <- data.frame(rep(c("s_disagree", "disagree", "agree", "s_agree"), times = 31))
colnames(t_ans3) <- "ans"
t_ans4 <- data.frame(rep(c("none", "rarely", "some", "most"), times = 1))
colnames(t_ans4) <- "ans"
t_ans5 <- data.frame(rep(c("s_disagree", "disagree", "agree", "s_agree"), times = 25))
colnames(t_ans5) <- "ans"
t_ans6 <- data.frame(rep(c("no_influence", "little", "moderate", "great_deal"), times = 5))
colnames(t_ans6) <- "ans"
t_ans7 <- data.frame(rep(c("v_dissatisfied", "dissatisfied", "satisfied", "v_satisfied", "idk"), times = 2))
colnames(t_ans7) <- "ans"
t_ans8 <- data.frame(rep(c("early_childhood", "social_studies", "science", "ELA", "math", "all", "other"), times = 1))
colnames(t_ans8) <- "ans"
t_ans9 <- data.frame(rep(c("s_disagree", "disagree", "agree", "s_agree"), times = 9))
colnames(t_ans9) <- "ans"
t_ans10 <- data.frame(rep(c("s_disagree", "disagree", "agree", "s_agree", "N/A"), times = 7))
colnames(t_ans10) <- "ans"
t_ans11 <- data.frame(rep(c("none", "some", "lot", "all"), times = 14))
colnames(t_ans11) <- "ans"
t_ans12 <- data.frame(rep(c("none", "some", "lot", "all", "idk"), times = 8))
colnames(t_ans12) <- "ans"
t_ans13 <- data.frame(rep(c("early_childhood", "elementary", "middle", "high"), times = 1))
colnames(t_ans13) <- "ans"
t_ans14 <- data.frame(rep(c("s_disagree", "disagree", "agree", "s_agree"), times = 10))
colnames(t_ans14) <- "ans"
t_ans15 <- data.frame(rep(c("s_disagree", "disagree", "agree", "s_agree", "idk"), times = 8))
colnames(t_ans15) <- "ans"
t_ans <- do.call("rbind", list(t_ans1, t_ans2, t_ans3, t_ans4, t_ans5, t_ans6, t_ans7, t_ans8, t_ans9, t_ans10, t_ans11, t_ans12, t_ans13, t_ans14, t_ans15))
t_colnames <- cbind(t_colnames, t_ans)
t_col <- paste0(t_colnames$questions, "-", t_colnames$ans)
t <- c("DBN", "School Name", "teacher_rr")
t_col <- append(t, t_col)
colnames(teacher) <- t_col
teacher <- replace(teacher, teacher == "N/A", NA)
teacher <- teacher %>%
  slice(-c(1,2))
teacher[3:579] = as.data.frame(sapply(teacher[3:579], as.numeric))
```

A example of teachers' response after data wrangling:
```{r}
head(teacher)
```
## Categorizing data based on survey questions

The survey questions included in this survey is comprehensive and difficult to manage. After reading through our survey questions, based on the survey questions, we have decided to categorize the data into different categories, and choose to analyze several categories based on our interests and whether there is sufficient data support. 

We realized that categorizing data based on survey questions could be highly objective and admit it as a limitation. We are open to any discussions and advice on categorizing survey questions.

Several questions are directly removed during the categorizing process. We have removed question 3, 4b, 4h, 14, 15, 16, 24, 25 from the teacher's survey either because it's not particularly relevant to survey questions from students' and parents' perspective, or due to significant amount of NAs. Questions 5d, 5e, 7, 8, 9, 10 are removed from the parents' dataset due to similar reasons or because some questions are targeted towards specific populations (eg. pre-k, high school). Some questions may be removed in latter process due to the inconsistencies in answer choices under the same category of questions. For example, while both question a and b falls under the same category, question a may have five answer choices while question b only have four answer choices.

After discussion, here are some example of the aspects we have decided to look into are teaching quality (from all perspectives of students, parents, and teachers), student performance (based on the feedback of teachers), communication between school and family (mainly based on the response from parents and teachers), and lastly, we'll look into the characteristics that may contribute to teaching quality, for example, trust and respect between teachers.

```{r}
# Survey Questions focusing on the teaching quality of teachers
s_teachingquality <- select(student, c(1:3, 59:98)) %>%
  mutate(type = "student") %>%
  mutate(none = rowSums(select(., ends_with("none")), na.rm=TRUE)) %>%
  mutate(few = rowSums(select(., ends_with("few")), na.rm=TRUE)) %>%
  mutate(most = rowSums(select(., ends_with("most")), na.rm=TRUE)) %>%
  mutate(all = rowSums(select(., ends_with("all")), na.rm=TRUE)) %>%
  select(c(1:3, 44:48))

t_teachingquality <- select(teacher, c(1:3, 8:23, 180:183, 236:291, 329:399, 456: 465)) %>%
  mutate(type = "teacher") %>%
  mutate(none = rowSums(select(., ends_with("none")), na.rm=TRUE)) %>%
  mutate(few = rowSums(select(., ends_with("some")), na.rm=TRUE)) %>%
  mutate(most = rowSums(select(., ends_with("a_lot")), na.rm=TRUE)) %>%
  mutate(most = rowSums(select(., ends_with("lot")), na.rm=TRUE)) %>%
  mutate(all = rowSums(select(., ends_with("all")), na.rm=TRUE)) %>%
  mutate(idk = rowSums(select(., ends_with("idk")), na.rm=TRUE)) %>%
  mutate(NAs= rowSums(select(., ends_with("N/A")), na.rm=TRUE)) %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  select(c(1:3, 161:171))

p_teachingquality <- select(parent, c(1:3, 120:129)) %>%
  mutate(type = "parent") %>%
  mutate(v_dissatisfied = rowSums(select(., ends_with("v_dissatisfied")), na.rm=TRUE)) %>%
  mutate(dissatisfied = rowSums(select(., ends_with("dissatisfied")), na.rm=TRUE)) %>%
  mutate(satisfied = rowSums(select(., ends_with("satisfied")), na.rm=TRUE)) %>%
  mutate(v_satisfied = rowSums(select(., ends_with("v_satisfied")), na.rm=TRUE)) %>%
  mutate(idk = rowSums(select(., ends_with("idk")), na.rm=TRUE)) %>%
  select(c(1:3, 14:19))

# Teachers have rated student performance, which is hypothesized to be positively correlated with teaching quality
t_sperformance <- select(teacher, c(1:3, 400:419, 436:455, 486:490)) %>%
  mutate(type = "teacher") %>%
  mutate(none = rowSums(select(., ends_with("none")), na.rm=TRUE)) %>%
  mutate(some = rowSums(select(., ends_with("some")), na.rm=TRUE)) %>%
  mutate(lot = rowSums(select(., ends_with("lot")), na.rm=TRUE)) %>%
  mutate(all = rowSums(select(., ends_with("all")), na.rm=TRUE)) %>%
  mutate(idk = rowSums(select(., ends_with("idk")), na.rm=TRUE)) %>%
  select(c(1:3, 49:54))
```

```{r}
# Survey questions focusing on activity or programs provided by school
s_activity <- select(student, c(1:13)) %>%
  mutate(type = "student") %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  mutate(idk = rowSums(select(., ends_with("idk")), na.rm=TRUE)) %>%
  select(c(1:3, 14:19))

t_activity <- select(teacher, c(1:3, 196:203)) %>%
  mutate(type = "teacher") %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  select(c(1:3, 12:16))

p_activity <- select(parent, c(1:3, 67:71)) %>%
  mutate(type = "parent") %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  mutate(idk = rowSums(select(., ends_with("idk")), na.rm=TRUE)) %>%
  select(c(1:3, 9:14))
```

```{r}
# Survey questions focusing on the level of difficulty on what is taught in school
s_difficulty <- select(student, c(1:3, 135:146)) %>%
  mutate(type = "student") %>%
  mutate(none = rowSums(select(., ends_with("none")), na.rm=TRUE)) %>%
  mutate(few = rowSums(select(., ends_with("few")), na.rm=TRUE)) %>%
  mutate(most = rowSums(select(., ends_with("most")), na.rm=TRUE)) %>%
  mutate(all = rowSums(select(., ends_with("all")), na.rm=TRUE)) %>%
  select(c(1:3, 16:20))

t_difficulty <-  select(teacher, c(1:3, 420:423, 428:431)) %>%
  mutate(type = "teacher") %>%
  mutate(none = rowSums(select(., ends_with("none")), na.rm=TRUE)) %>%
  mutate(few = rowSums(select(., ends_with("some")), na.rm=TRUE)) %>%
  mutate(most = rowSums(select(., ends_with("lot")), na.rm=TRUE)) %>%
  mutate(all = rowSums(select(., ends_with("all")), na.rm=TRUE)) %>%
  select(c(1:3, 12:16)) 
```

```{r}
# Survey questions on school discipline
s_disciplie <- select(student, c(1:3, 155:170)) %>%
  mutate(type = "student") %>%
  mutate(none = rowSums(select(., ends_with("none")), na.rm=TRUE)) %>%
  mutate(few = rowSums(select(., ends_with("few")), na.rm=TRUE)) %>%
  mutate(most = rowSums(select(., ends_with("most")), na.rm=TRUE)) %>%
  mutate(all = rowSums(select(., ends_with("all")), na.rm=TRUE)) %>%
  select(c(1:3, 20:24))

t_discipline <- select(teacher, c(1:3, 4:7, 168:171, 184:187, 424:427, 432:435)) %>%
  mutate(type = "teacher") %>%
  mutate(none = rowSums(select(., ends_with("none")), na.rm=TRUE)) %>%
  mutate(few = rowSums(select(., ends_with("some")), na.rm=TRUE)) %>%
  mutate(most = rowSums(select(., ends_with("a_lot")), na.rm=TRUE)) %>%
  mutate(most = rowSums(select(., ends_with("lot")), na.rm=TRUE)) %>%
  mutate(all = rowSums(select(., ends_with("all")), na.rm=TRUE)) %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  select(c(1:3, 24:32))
```

```{r}
# Survey questions on inclusion and diversity
s_inclusion <- select(student, c(1:3, 24:58, 127:130)) %>%
  mutate(type = "student") %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  mutate(idk = rowSums(select(., ends_with("idk")), na.rm=TRUE)) %>%
  select(c(1:3, 36:41))

t_inclusion <- select(teacher, c(1:3, 24:63, 152:155, 160:167)) %>%
  mutate(type = "teacher") %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  mutate(idk = rowSums(select(., ends_with("idk")), na.rm=TRUE)) %>%
  select(c(1:3, 56:61))
```

```{r}
# Survey question on trust
s_trust <- select(student, c(1:3, 103:122)) %>%
  mutate(type = "student") %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  select(c(1:3, 24:28))

t_trust <- select(teacher, c(1:3, 92:99, 120:135)) %>%
  mutate(type = "teacher") %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  select(c(1:3, 28:32))
```

```{r}
# Survey question on motivation
s_self_motivation <- select(student, c(1:3, 171:190)) %>%
  mutate(type = "student") %>%
  mutate(none = rowSums(select(., ends_with("none")), na.rm=TRUE)) %>%
  mutate(few = rowSums(select(., ends_with("few")), na.rm=TRUE)) %>%
  mutate(most = rowSums(select(., ends_with("most")), na.rm=TRUE)) %>%
  mutate(all = rowSums(select(., ends_with("all")), na.rm=TRUE)) %>%
  select(c(1:3, 24:28))

t_self_motivation <- select(teacher, c(1:3, 84:87)) %>%
  mutate(type = "teacher") %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  select(c(1:3, 8:12))
```

```{r}
# survey question on repect
s_respect <- select(student, c(1:3, 19:23)) %>%
  mutate(type = "student") %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  mutate(idk = rowSums(select(., ends_with("idk")), na.rm=TRUE)) %>%
  select(c(1:3, 9:14))

t_respect <- select(teacher, c(1:3, 100:111, 116:119, 136:147, 156:159)) %>%
  mutate(type = "teacher") %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  select(c(1:3, 36:40))
```

```{r}
# Survey question on collaboration
s_collaboration <- select(student, c(1:3, 147:150)) %>%
  mutate(type = "student") %>%
  mutate(none = rowSums(select(., ends_with("none")), na.rm=TRUE)) %>%
  mutate(few = rowSums(select(., ends_with("few")), na.rm=TRUE)) %>%
  mutate(most = rowSums(select(., ends_with("most")), na.rm=TRUE)) %>%
  mutate(all = rowSums(select(., ends_with("all")), na.rm=TRUE)) %>%
  select(c(1:3, 8:12))

t_collaboration <- select(teacher, c(1:3, 148:151, 192:195, 204:215)) %>%
  mutate(type = "teacher") %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  select(c(1:3, 24:28))

p_collaboration <- select(parent, c(1:3, 92:96)) %>%
  mutate(type = "parent") %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  mutate(idk = rowSums(select(., ends_with("idk")), na.rm=TRUE)) %>%
  select(c(1:3, 10:14))
```

```{r}
# Survey question on cleanning
s_clean <- select(student, c(1:3, 14:18)) %>%
  mutate(type = "student") %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  mutate(idk = rowSums(select(., ends_with("idk")), na.rm=TRUE)) %>%
  select(c(1:3, 9:14))

t_clean <- select(teacher, c(1:3, 172:175)) %>%
  mutate(type = "teacher") %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  select(c(1:3, 8:12))

p_clean <- select(parent, c(1:3, 82:86)) %>%
  mutate(type = "parent") %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  mutate(idk = rowSums(select(., ends_with("idk")), na.rm=TRUE)) %>%
  select(c(1:3, 10:14))
```

```{r}
# Survey question on safety
s_safety <- select(student, c(1:3, 131:134, 191:206)) %>%
  mutate(type = "student") %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  select(c(1:3, 24:28))

t_safety <- select(teacher, c(1:3, 176:179, 524:539)) %>%
  mutate(type = "teacher") %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  select(c(1:3, 24:28))

p_safety <- select(parent, c(1:3, 77:81, 87:91)) %>%
  mutate(type = "parent") %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  mutate(idk = rowSums(select(., ends_with("idk")), na.rm=TRUE)) %>%
  select(c(1:3, 14:19))
```

```{r}
# Survey question on bullying, harrasement, and any aggresive behaviors
s_aggresive_behavior <- select(student, c(1:3, 207:238))  %>%
  mutate(type = "student") %>%
  mutate(none = rowSums(select(., ends_with("none")), na.rm=TRUE)) %>%
  mutate(rarely = rowSums(select(., ends_with("rarely")), na.rm=TRUE)) %>%
  mutate(some = rowSums(select(., ends_with("some")), na.rm=TRUE)) %>%
  mutate(most = rowSums(select(., ends_with("most")), na.rm=TRUE)) %>%
  select(c(1:3, 36:40))

t_aggresive_behavior <- select(teacher, c(1:3, 188:191))  %>%
  mutate(type = "teacher") %>%
  mutate(none = rowSums(select(., ends_with("none")), na.rm=TRUE)) %>%
  mutate(rarely = rowSums(select(., ends_with("rarely")), na.rm=TRUE)) %>%
  mutate(some = rowSums(select(., ends_with("some")), na.rm=TRUE)) %>%
  mutate(most = rowSums(select(., ends_with("most")), na.rm=TRUE)) %>%
  select(c(1:3, 8:12))
```

```{r}
# Survey question on family related questions
t_family <- select(teacher, c(1:3, 216:235, 516:523)) %>%
  mutate(type = "teacher") %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  select(c(1:3, 32:36))

p_family <- select(parent, c(1:3, 4:66, 72:76, 97:119, 140:147)) %>%
  mutate(type = "parent") %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  mutate(idk = rowSums(select(., ends_with("idk")), na.rm=TRUE)) %>%
  mutate(never = rowSums(select(., ends_with("never")), na.rm=TRUE)) %>%
  mutate(rarely = rowSums(select(., ends_with("rarely")), na.rm=TRUE)) %>%
  mutate(some = rowSums(select(., ends_with("sometimes")), na.rm=TRUE)) %>%
  mutate(often = rowSums(select(., ends_with("often")), na.rm=TRUE)) %>%
  mutate(v_unlikely = rowSums(select(., ends_with("v_unlikely")), na.rm=TRUE)) %>%
  mutate(unlikely = rowSums(select(., ends_with("unlikely")), na.rm=TRUE)) %>%
  mutate(likely = rowSums(select(., ends_with("likely")), na.rm=TRUE)) %>%
  mutate(v_likely = rowSums(select(., ends_with("v_likely")), na.rm=TRUE)) %>%
  mutate(v_dissatisfied = rowSums(select(., ends_with("v_dissatisfied")), na.rm=TRUE)) %>%
  mutate(dissatisfied = rowSums(select(., ends_with("dissatisfied")), na.rm=TRUE)) %>%
  mutate(satisfied = rowSums(select(., ends_with("satisfied")), na.rm=TRUE)) %>%
  mutate(v_satisfied = rowSums(select(., ends_with("v_satisfied")), na.rm=TRUE)) %>%
  select(c(1:3, 113:120))
```

```{r}
# Survey question on other skills, eg. critical thinking
s_lifeskill <- select(student, c(1:3, 123:126, 151:154)) %>%
  mutate(type = "teacher") %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  mutate(none = rowSums(select(., ends_with("none")), na.rm=TRUE)) %>%
  mutate(few = rowSums(select(., ends_with("few")), na.rm=TRUE)) %>%
  mutate(most = rowSums(select(., ends_with("most")), na.rm=TRUE)) %>%
  mutate(all = rowSums(select(., ends_with("all")), na.rm=TRUE)) %>%
  select(c(1:3, 12:20))

t_lifeskill <- select(teacher, c(1:3, 466:490)) %>%
  mutate(type = "teacher") %>%
  mutate(none = rowSums(select(., ends_with("none")), na.rm=TRUE)) %>%
  mutate(few = rowSums(select(., ends_with("some")), na.rm=TRUE)) %>%
  mutate(most = rowSums(select(., ends_with("lot")), na.rm=TRUE)) %>%
  mutate(all = rowSums(select(., ends_with("all")), na.rm=TRUE)) %>%
  mutate(idk = rowSums(select(., ends_with("idk")), na.rm=TRUE)) %>%
  select(c(1:3, 29:34))
```

```{r}
# survey question on any future planning
s_future <- select(student, c(1:3, 99:102, 239:272)) %>%
  mutate(type = "student") %>%
  mutate(NAs = rowSums(select(., ends_with("N/A")), na.rm=TRUE)) %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  select(c(1:3, 42:47))

t_future <- select(teacher, c(1:3, 540:579)) %>%
  mutate(type = "teacher") %>%
  mutate(idk = rowSums(select(., ends_with("idk")), na.rm=TRUE)) %>%
  mutate(s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  select(c(1:3, 44:49))
```

## Datasets that we decide to analyze

Note that some answer choice are renamed due to inconsistencies between questions. Additionally, some questions are deleted due to the same reason.

### Communication with families from teachers' and parents' perspectives
```{r}
t_family <- select(teacher, c(1:3, 216:235, 516:523)) %>%
  mutate(t_s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(t_s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(t_agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(t_disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  select(c(1:3, 32:35))

p_family <- select(parent, c(1:3, 4:66, 72:76, 97:107)) %>%
  mutate(p_s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(p_s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(p_agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(p_disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  mutate(p_idk = rowSums(select(., ends_with("idk")), na.rm=TRUE)) %>%
  select(c(1:3, 83:87))

family <- t_family %>%
  inner_join(p_family)

saveRDS(family, "family")
```

```{r}
head(family)
```

### Teaching quality and student performance
```{r}
# Survey Questions focusing on the teaching quality of teachers
s_teachingquality <- select(student, c(1:3, 59:98)) %>%
  mutate(st_v_negative = rowSums(select(., ends_with("none")), na.rm=TRUE)) %>%
  mutate(st_v_positive = rowSums(select(., ends_with("few")), na.rm=TRUE)) %>%
  mutate(st_positive = rowSums(select(., ends_with("most")), na.rm=TRUE)) %>%
  mutate(st_negative = rowSums(select(., ends_with("all")), na.rm=TRUE)) %>%
  select(c(1:3, 44:47))

t_teachingquality <- select(teacher, c(1:3, 180:183, 236:291, 329:399)) %>%
  mutate(t_NAs= rowSums(select(., ends_with("N/A")), na.rm=TRUE)) %>%
  mutate(t_v_negative = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(t_v_positive = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(t_positive = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(t_negative = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  select(c(1:3, 135:139))

p_teachingquality <- select(parent, c(1:3, 120:129)) %>%
  mutate(p_v_neagtive = rowSums(select(., ends_with("v_dissatisfied")), na.rm=TRUE)) %>%
  mutate(p_negative = rowSums(select(., ends_with("dissatisfied")), na.rm=TRUE)) %>%
  mutate(p_positive = rowSums(select(., ends_with("satisfied")), na.rm=TRUE)) %>%
  mutate(p_v_positive = rowSums(select(., ends_with("v_satisfied")), na.rm=TRUE)) %>%
  mutate(p_idk = rowSums(select(., ends_with("idk")), na.rm=TRUE)) %>%
  select(c(1:3, 14:18))

teachingquality <- p_teachingquality %>%
  inner_join(t_teachingquality)
teachingquality <- teachingquality %>%
  inner_join(s_teachingquality)

saveRDS(teachingquality, "teachingquality")

# Teachers have rated student performance, which is hypothesized to be positively correlated with teaching quality
t_sperformance <- select(teacher, c(1:3, 400:419, 436:455, 486:490)) %>%
  mutate(t_none = rowSums(select(., ends_with("none")), na.rm=TRUE)) %>%
  mutate(t_some = rowSums(select(., ends_with("some")), na.rm=TRUE)) %>%
  mutate(t_lot = rowSums(select(., ends_with("lot")), na.rm=TRUE)) %>%
  mutate(t_all = rowSums(select(., ends_with("all")), na.rm=TRUE)) %>%
  mutate(t_idk = rowSums(select(., ends_with("idk")), na.rm=TRUE)) %>%
  select(c(1:3, 49:53))

saveRDS(t_sperformance, "t_sperformance")
```

```{r}
head(teachingquality)
head(t_sperformance)
```

### Trust, respect, and collaboration between teachers
```{r}
t_trust <- select(teacher, c(1:3, 92:99, 120:135)) %>%
  mutate(t_s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(t_s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(t_agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(t_disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  select(c(1:3, 28:31))

t_collaboration <- select(teacher, c(1:3, 148:151, 192:195, 204:215)) %>%
  mutate(c_s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(c_s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(c_agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(c_disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  select(c(1:3, 24:27))

t_respect <- select(teacher, c(1:3, 100:111, 116:119, 136:147, 156:159)) %>%
  mutate(r_s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(r_s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(r_agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(r_disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  select(c(1:3, 36:39))

teacher_tcr <- t_respect %>%
  inner_join(t_collaboration)
teacher_tcr <- teacher_tcr %>%
  inner_join(t_trust)

saveRDS(teacher_tcr, "teacher_tcr")
```

```{r}
head(teacher_tcr)
```

### Diversity and inclusion from students' and teachers' perspectives
```{r}
# Survey questions on inclusion and diversity
s_inclusion <- select(student, c(1:3, 24:58, 127:130)) %>%
  mutate(st_s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(st_s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(st_agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(st_disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  mutate(st_idk = rowSums(select(., ends_with("idk")), na.rm=TRUE)) %>%
  select(c(1:3, 43:47))

t_inclusion <- select(teacher, c(1:3, 24:63, 152:155, 160:167)) %>%
  mutate(t_s_disagree = rowSums(select(., ends_with("s_disagree")), na.rm=TRUE)) %>%
  mutate(t_s_agree = rowSums(select(., ends_with("s_agree")), na.rm=TRUE)) %>%
  mutate(t_agree = rowSums(select(., ends_with("agree")), na.rm=TRUE)) %>%
  mutate(t_disagree = rowSums(select(., ends_with("disagree")), na.rm=TRUE)) %>%
  mutate(t_idk = rowSums(select(., ends_with("idk")), na.rm=TRUE)) %>%
  select(c(1:3, 56:60))
inclusion <- t_inclusion %>%
  inner_join(s_inclusion)

saveRDS(inclusion, "inclusion")
```

```{r}
head(inclusion)
```

### Bullying, harrasement, and any aggresive behaviors from teachers' and students' perspective
```{r}
# Survey question on bullying, harrasement, and any aggresive behaviors
s_aggresive_behavior <- select(student, c(1:3, 207:238))  %>%
  mutate(st_none = rowSums(select(., ends_with("none")), na.rm=TRUE)) %>%
  mutate(st_rarely = rowSums(select(., ends_with("rarely")), na.rm=TRUE)) %>%
  mutate(st_some = rowSums(select(., ends_with("some")), na.rm=TRUE)) %>%
  mutate(st_most = rowSums(select(., ends_with("most")), na.rm=TRUE)) %>%
  select(c(1:3, 36:39))

t_aggresive_behavior <- select(teacher, c(1:3, 188:191))  %>%
  mutate(t_none = rowSums(select(., ends_with("none")), na.rm=TRUE)) %>%
  mutate(t_rarely = rowSums(select(., ends_with("rarely")), na.rm=TRUE)) %>%
  mutate(t_some = rowSums(select(., ends_with("some")), na.rm=TRUE)) %>%
  mutate(t_most = rowSums(select(., ends_with("most")), na.rm=TRUE)) %>%
  select(c(1:3, 8:11))

aggresive_behavior <- t_aggresive_behavior %>%
  inner_join(s_aggresive_behavior)

saveRDS(aggresive_behavior, "ab")
```

```{r}
head(aggresive_behavior)
```

