

# Results

## Distribution of School Scores

Before we make any comparison between NYC schools, we firstly have a look at the distribution of our dataset, i.e. the distribution of school scores from students', teachers' and parents' perspective. In order to do that, we make density plots of the scores faceted by these five components.(we drop `supportive environment score` because we know from chapter 4 that it has nearly 100% missing values)

```{r}
library(readxl)
library(tidyverse)
warnings('off')
options (warn = -1)
student <- read_excel("Student.xlsx")
teacher<-read_excel("Teacher.xlsx")
parent<-read_excel("Parent.xlsx")
student_ <- student %>%
  rename(student_rr = `Total Student Response Rate`) %>%
  rename(parent_rr = `Total Parent \r\nResponse Rate`) %>%
  rename(teacher_rr = `Total Teacher Response Rate`) %>%
  rename(name = `School Name`) %>%
  rename(trust = `Trust Score`) %>%
  rename(collab_teachers = `Collaborative Teachers Score`) %>%
  rename(effective_schlead = `Effective School Leadership Score`) %>%
  rename(rig_instruction = `Rigorous Instruction Score`) %>%
  rename(supp_env = `Supportive Environment Score`) %>%
  rename(family_communityties = `Strong Family-Community Ties Score`)
teacher_ <- teacher %>%
  rename(student_rr = `Total Student Response Rate`) %>%
  rename(parent_rr = `Total Parent \r\nResponse Rate`) %>%
  rename(teacher_rr = `Total Teacher Response Rate`) %>%
  rename(name = `School Name`) %>%
  rename(t_trust = `Trust Score`) %>%
  rename(t_collab_teachers = `Collaborative Teachers Score`) %>%
  rename(t_effective_schlead = `Effective School Leadership Score`) %>%
  rename(t_rig_instruction = `Rigorous Instruction Score`) %>%
  rename(t_supp_env = `Supportive Environment Score`) %>%
  rename(t_family_communityties = `Strong Family-Community Ties Score`)
parent_ <- parent %>%
  rename(student_rr = `Total Student Response Rate`) %>%
  rename(parent_rr = `Total Parent \r\nResponse Rate`) %>%
  rename(teacher_rr = `Total Teacher Response Rate`) %>%
  rename(name = `School Name`) %>%
  rename(p_trust = `Trust Score`) %>%
  rename(p_collab_teachers = `Collaborative Teachers Score`) %>%
  rename(p_effective_schlead = `Effective School Leadership Score`) %>%
  rename(p_rig_instruction = `Rigorous Instruction Score`) %>%
  rename(p_supp_env = `Supportive Environment Score`) %>%
  rename(p_family_communityties = `Strong Family-Community Ties Score`)
st = merge(student_, teacher_,by = c("DBN","name","parent_rr","teacher_rr","student_rr"))
stp = merge(st,parent_,by = c("DBN","name","parent_rr","teacher_rr","student_rr"))
stp$collab_teachers <- as.numeric(stp$collab_teachers)
stp$effective_schlead<- as.numeric(stp$effective_schlead)
stp$rig_instruction <- as.numeric(stp$rig_instruction)
stp$supp_env <- as.numeric(stp$supp_env)
stp$family_communityties <- as.numeric(stp$family_communityties)
stp$trust <- as.numeric(stp$trust)
stp$t_collab_teachers <- as.numeric(stp$t_collab_teachers)
stp$t_effective_schlead<- as.numeric(stp$t_effective_schlead)
stp$t_rig_instruction <- as.numeric(stp$t_rig_instruction)
stp$t_supp_env <- as.numeric(stp$t_supp_env)
stp$t_family_communityties <- as.numeric(stp$t_family_communityties)
stp$t_trust <- as.numeric(stp$t_trust)
stp$p_collab_teachers <- as.numeric(stp$p_collab_teachers)
stp$p_effective_schlead<- as.numeric(stp$p_effective_schlead)
stp$p_rig_instruction <- as.numeric(stp$p_rig_instruction)
stp$p_supp_env <- as.numeric(stp$p_supp_env)
stp$p_family_communityties <- as.numeric(stp$p_family_communityties)
stp$p_trust <- as.numeric(stp$p_trust)
stp$student_rr<-as.numeric(stp$student_rr)
tidydata<-stp %>%
  pivot_longer(cols =!c(name,DBN,parent_rr,student_rr,teacher_rr), names_to = "aspect",values_to = "score")

```
```{r}
tidydata_t <- tidydata %>%
              filter(aspect =="collab_teachers"|aspect =="effective_schlead"|aspect =="rig_instruction"|aspect == "family_communityties"|aspect == "trust")
ggplot(tidydata_t,aes(x = score,y = ..density..))+
  geom_histogram(bins = 40, colour = "#80593D",fill = "#9FC29F")+
  geom_density(color = "#3D6480")+
  facet_wrap(~aspect)+
  ggtitle("Result in School Quality")
```
We know from the plot that the distribution of school scores in these five aspects are not normally distributed, in fact, they are left-skewed, with long-tail data distributing in the left side of the plot. 

## Top 10 performance schools

### Top 10 schools in five aspects

Firstly, we sort the schools according to the five aforementioned aspects. In this way, we made a leaderboard for Top 10 Schools with the most collaborative teachers, Top 10 Schools with the most effective School Leadership, Top 10 Schools with the most Trust beween people, Top 10 Schools with the most rigid instructions, and Top 10 Schools with the Strongest Family Community Ties

```{r}
library(dplyr)
library(ggplot2)
student_$collab_teachers<-as.numeric(student_$collab_teachers)
score_sorted <- student_ %>% arrange(desc(collab_teachers))
top10<-head(score_sorted,10)

p<-ggplot(data = top10,aes(collab_teachers, fct_reorder(name, collab_teachers),label = collab_teachers)) + geom_point() + ggtitle('Top 10 Schools with the most collaborative teachers') + ylab('School Name')
  
p+geom_label()+xlab("School Names")+theme(axis.text.y=element_text(angle=0,hjust = 1,size = 4))+ggtitle("Top 10 Schools with the most collaborative teachers")

```
```{r}
student_$effective_schlead<-as.numeric(student_$effective_schlead)
score_sorted_1 <- student_ %>% arrange(desc(effective_schlead))
top10_1<-head(score_sorted_1,10)

p<-ggplot(data = top10_1,aes(effective_schlead, fct_reorder(name, effective_schlead),label = effective_schlead)) + geom_point() +  ylab('School Name')
  
p+geom_label()+xlab("School Names")+theme(axis.text.y=element_text(angle=0,hjust = 1,size = 4))+ggtitle("Top 10 Schools with the most effective School Leadership")
```
```{r}
student_$trust<-as.numeric(student_$trust)
score_sorted_1 <- student_ %>% arrange(desc(trust))
top10_1<-head(score_sorted_1,10)

p<-ggplot(data = top10_1,aes(trust, fct_reorder(name, trust),label = trust)) + geom_point() +  ylab('School Name')
  
p+geom_label()+xlab("School Names")+theme(axis.text.y=element_text(angle=0,hjust = 1,size = 4))+ggtitle("Top 10 Schools with the most Trust beween people")

```
```{r}
student_$rig_instruction<-as.numeric(student_$rig_instruction)
score_sorted_1 <- student_ %>% arrange(desc(rig_instruction))
top10_1<-head(score_sorted_1,10)

p<-ggplot(data = top10_1,aes(rig_instruction, fct_reorder(name, rig_instruction),label = rig_instruction)) + geom_point() +  ylab('School Name')
  
p+geom_label()+xlab("School Names")+theme(axis.text.y=element_text(angle=0,hjust = 1,size = 4))+ggtitle("Top 10 Schools with the most rigid instructions")
```

```{r}
student_$family_communityties<-as.numeric(student_$family_communityties)
score_sorted_1 <- student_ %>% arrange(desc(family_communityties))
top10_1<-head(score_sorted_1,10)

p<-ggplot(data = top10_1,aes(family_communityties, fct_reorder(name, family_communityties),label = family_communityties)) + geom_point() +  ylab('School Name')
  
p+geom_label()+xlab("School Names")+theme(axis.text.y=element_text(angle=0,hjust = 1,size = 3))+ggtitle("Top 10 Schools with the Strongest Family Community Ties")

```

### Top 10 Schools with the highest comprehensive scores

Sometimes it is necessary to evaluate the schools in a more comprehensive way. Therefore, we take all the five aspects into consideration and calculate a comprehensive school performance score by taking the average of all the scores in five aspects. Then we made a leaderboard of the "Best" 10 Schools in NYC. 

```{r}
library(tidyverse)
avg <- student_ %>% mutate(total_score = (collab_teachers+effective_schlead+rig_instruction+family_communityties+trust)/5) %>%
  arrange(desc(total_score))
top10_1<-head(avg,10)

p<-ggplot(data = top10_1,aes(total_score, fct_reorder(name, total_score),label = total_score)) + geom_point() +  ylab('School Name')
  
p+geom_label()+xlab("School Names")+theme(axis.text.y=element_text(angle=0,hjust = 1,size = 4))+ggtitle("Top 10 Schools with the highest comprehensive scores")

```

The best 10 schools in NYC are:
```{r}
top10_1$name
```

## Dependency Relationships analysis

Apart from the scores derived from the result given by  Department of Education of NYC, we also evaluate the performance of each school from the perspective of students, teachers and parents according to their answers to the questionnaire directly. In this section, we are going to look at the relationship of school scores given from different perspectives. 

### Do Teachers and Parents feel the same about Family-Community bond?

Both teachers and parents have answered some questions about their feelings about the family-community bond in their schools. For example, in the questionnaire for teachers, there are several statements like "teachers understand families' problems and concerns."; in the questionnaire for parents, there are statements like "School staff regularly communicate with me about how I can help my child learn.". Parents and teachers are asked to give the degree in which they agree to such statements, such as "strongly agree","agree","disagree","strongly disagree","idk". In this way, we are able to analysis whether teachers and parents feel the same about the family-community bond in their schools. 

In order to make our analysis easier, we firstly derive a family-community bond score for each school from parents' and teachers' point of view respectively. More specifically, we calculate the percentage of `strongly agree`,`agree`,`disagree`,`strongly disagree`,`idk`, and add +2 points for `strongly agree`, +1 point for `agree`, -1 point for `disagree`, -2 points for `strongly disagree` and +0 point for `idk`. 

The scores given by teachers and parents are clearly positively correlated:

```{r}
family<-read_rds("family")
family_<-family %>% mutate(t_s_disagree_percent = t_s_disagree/(t_s_disagree+t_s_agree+t_agree+t_disagree)) %>% mutate(t_disagree_percent = t_disagree/(t_s_disagree+t_s_agree+t_agree+t_disagree))%>% mutate(t_agree_percent = t_agree/(t_s_disagree+t_s_agree+t_agree+t_disagree))%>% mutate(t_s_agree_percent = t_s_agree/(t_s_disagree+t_s_agree+t_agree+t_disagree))%>% mutate(t_score = 2*t_s_agree_percent+1*t_agree_percent-1*t_disagree_percent-2*t_s_disagree_percent) %>% mutate(p_s_disagree_percent = p_s_disagree/(p_s_disagree+p_s_agree+p_agree+p_disagree)) %>% mutate(p_disagree_percent = p_disagree/(p_s_disagree+p_s_agree+p_agree+p_disagree))%>% mutate(p_agree_percent = p_agree/(p_s_disagree+p_s_agree+p_agree+p_disagree))%>% mutate(p_s_agree_percent = p_s_agree/(p_s_disagree+p_s_agree+p_agree+p_disagree))%>% mutate(p_score = 2*p_s_agree_percent+1*p_agree_percent-1*p_disagree_percent-2*p_s_disagree_percent)

ggplot(data = family_,aes(x = t_score,y = p_score))+
  geom_point(color = "#9FC29F")+theme_grey(18)+xlab("score given by teachers")+ylab("score given by parents")
```
The correlation coefficient is:

```{r}
family_rmna<-family_[complete.cases(family_[,c(18,20)]),]
cor(family_rmna$t_score,family_rmna$p_score)
```

### Do teachers and students feel the same about student inclusion?

Teachers and students have answered some questions about their feelings towards the student inclusion in their schools from their own perspectives. In this way, we are able to analysis whether teachers and students feel the same about student inclusion. 

In order to make our analysis easier, we firstly calculate a student inclusion score for each school from students' and teachers' point of view respectively, using the formula mentioned in 5.3.1.

The scores given by students and teachers are also positively correlated:

```{r}
inclusion<-read_rds("inclusion")
inclusion_<-inclusion %>% mutate(t_s_disagree_percent = t_s_disagree/(t_s_disagree+t_s_agree+t_agree+t_disagree)) %>% mutate(t_disagree_percent = t_disagree/(t_s_disagree+t_s_agree+t_agree+t_disagree))%>% mutate(t_agree_percent = t_agree/(t_s_disagree+t_s_agree+t_agree+t_disagree))%>% mutate(t_s_agree_percent = t_s_agree/(t_s_disagree+t_s_agree+t_agree+t_disagree))%>% mutate(t_score = 2*t_s_agree_percent+1*t_agree_percent-1*t_disagree_percent-2*t_s_disagree_percent) %>% mutate(st_s_disagree_percent = st_s_disagree/(st_s_disagree+st_s_agree+st_agree+st_disagree)) %>% mutate(st_disagree_percent = st_disagree/(st_s_disagree+st_s_agree+st_agree+st_disagree))%>% mutate(st_agree_percent = st_agree/(st_s_disagree+st_s_agree+st_agree+st_disagree))%>% mutate(st_s_agree_percent = st_s_agree/(st_s_disagree+st_s_agree+st_agree+st_disagree))%>% mutate(st_score = 2*st_s_agree_percent+1*st_agree_percent-1*st_disagree_percent-2*st_s_disagree_percent)

ggplot(data = inclusion_,aes(x = t_score,y = st_score))+
  geom_point(color = "#9FC29F")+theme_grey(18)+xlab("score given by teachers")+ylab("score given by students")
```
The correlation coefficient is:

```{r}
inclusion_rmna<-inclusion_[complete.cases(inclusion_[,c(18,20)]),]
cor(inclusion_rmna$t_score,inclusion_rmna$st_score)
```
### Do teachers and students feel the same about aggressive behaviors?

Both teachers and parents have answered some questions about their feelings about the aggressive behaviors in their schools. The are asked to reply how frequent such aggressive behaviors happens, such as "none","rarely","some","most". In this way, we are able to analysis whether teachers and students feel the same about the aggressive behaviors in their schools. 

In order to make our analysis easier, we firstly derive a score for each school from parents' and teachers' point of view respectively. More specifically, we calculate the percentage of `none`,`rarely`,`some`,`most`, and add +2 points for `none`, +1 point for `rarely`, -1 point for `some`, -2 points for `most`.

The scores given by students and teachers are also positively correlated:

```{r}
ab <- read_rds("ab")
ab_<-ab %>%
  mutate(t_none_percent = t_none/(t_none+t_rarely+t_some+t_most)) %>%
  mutate(t_rarely_percent = t_rarely/(t_none+t_rarely+t_some+t_most))%>%
  mutate(t_some_percent = t_some/(t_none+t_rarely+t_some+t_most))%>%
  mutate(t_most_percent = t_most/(t_none+t_rarely+t_some+t_most))%>%
  mutate(t_score = 2*t_none_percent+1*t_rarely_percent-1*t_some_percent-2*t_most_percent)%>%
  mutate(st_none_percent = st_none/(st_none+st_rarely+st_some+st_most)) %>%
  mutate(st_rarely_percent = st_rarely/(st_none+t_rarely+st_some+st_most))%>%
  mutate(st_some_percent = st_some/(st_none+t_rarely+st_some+st_most))%>%
  mutate(st_most_percent = st_most/(st_none+st_rarely+st_some+st_most))%>%
  mutate(st_score = 2*st_none_percent+1*st_rarely_percent-1*st_some_percent-2*st_most_percent)
ggplot(data = ab_,aes(x = t_score,y = st_score))+
  geom_point(color = "#9FC29F")+theme_grey(18)+xlab("score given by teachers")+ylab("score given by students")
```

The correlation coefficient is:

```{r}
ab_rmna<-ab_[complete.cases(ab_[,c(17,22)]),]
cor(ab_rmna$t_score,ab_rmna$st_score)
```

## Do parents, students and teachers feel the same about teaching quality?

Students, teachers and parents have answered some questions about their feelings about the teaching quality in their schools. The are asked to reply to which degree they believe that the teachers demonstrate good teaching qualities, such as "strongly positive","positive","negative","strongly negative","i don't know". In this way, we are able to analysis whether parents, teachers and students feel the same about teaching quality.

In order to make our analysis easier, we firstly derive a score for each school from students', parents' and teachers' point of view respectively. More specifically, we calculate the percentage of `strongly positive`,`positive`,`negative`,`strongly negative`, and add +2 points for `strongly positive`, +1 point for `positive`, -1 point for `negative`, -2 points for `strongly negative`.

The relationship between the score given by parents, students and teachers are plotted in the following scatterplot:


```{r}
tq<-read_rds("teachingquality")
tq_<-tq %>%
  mutate(p_v_neagtive_percent = p_v_neagtive/(p_v_neagtive+p_negative+p_positive+p_v_positive+p_idk)) %>%
  mutate(p_negative_percent = p_negative/(p_v_neagtive+p_negative+p_positive+p_v_positive+p_idk))%>%
  mutate(p_positive_percent = p_positive/(p_v_neagtive+p_negative+p_positive+p_v_positive+p_idk))%>%
  mutate(p_v_positive_percent = p_v_positive/(p_v_neagtive+p_negative+p_positive+p_v_positive+p_idk))%>%
  mutate(p_score = 2*p_v_positive_percent+1*p_positive_percent-1*p_negative_percent-2*p_v_neagtive_percent)


tq_<-tq_ %>%
  mutate(t_v_negative_percent = t_v_negative/(t_v_negative+t_negative+t_positive+t_v_positive+t_NAs)) %>%
  mutate(t_negative_percent = t_negative/(t_v_negative+t_negative+t_positive+t_v_positive+t_NAs))%>%
  mutate(t_positive_percent = t_positive/(t_v_negative+t_negative+t_positive+t_v_positive+t_NAs))%>%
  mutate(t_v_positive_percent = t_v_positive/(t_v_negative+t_negative+t_positive+t_v_positive+t_NAs))%>%
  mutate(t_score = 2*t_v_positive_percent+1*t_positive_percent-1*t_negative_percent-2*t_v_negative_percent)


tq_<-tq_ %>%
  mutate(st_v_negative_percent = st_v_negative/(st_v_negative+st_negative+st_positive+st_v_positive)) %>%
  mutate(st_negative_percent = st_negative/(st_v_negative+st_negative+st_positive+st_v_positive))%>%
  mutate(st_positive_percent = st_positive/(st_v_negative+st_negative+st_positive+st_v_positive))%>%
  mutate(st_v_positive_percent = st_v_positive/(st_v_negative+st_negative+st_positive+st_v_positive))%>%
  mutate(st_score = 2*st_v_positive_percent+1*st_positive_percent-1*st_negative_percent-2*st_v_negative_percent)
```

```{r}
library(GGally)
 
data <- tq_ %>% select(t_score,p_score,st_score)
 
ggpairs(data, title="") 
```

The score given by teachers and parents are positively correlated, however, the score given by students are negatively correlated with the score given by teachers and parents. Moreover, students tend to give poor scores to their teachers while teachers and parents tend to give higher score to teaching quality. 

## The relationship between teachers' trust/collaboration/respect with teaching quality

In this survey, teachers are also asked several questions about their feelings towards the trust, collaboration and respect between teachers in their schools. We believe that a healthy environment in teacher community is beneficial to the teaching quality. Therefore, in this section we investigate whether our hypothesis is true. 


```{r}
teacher_tcr<-read_rds("teacher_tcr")
teacher_tcr_quality<-merge(teacher_tcr, tq_, by = "School Name")
teacher_tcr_quality_<-teacher_tcr_quality %>% mutate(r_s_disagree_percent = r_s_disagree/(r_s_disagree+r_s_agree+r_agree+r_disagree))%>%
  mutate(r_s_agree_percent = r_s_agree/(r_s_disagree+r_s_agree+r_agree+r_disagree))%>%
  mutate(r_agree_percent = r_agree/(r_s_disagree+r_s_agree+r_agree+r_disagree))%>%
  mutate(r_disagree_percent = r_disagree/(r_s_disagree+r_s_agree+r_agree+r_disagree))%>%
  mutate(respect_score = r_s_agree_percent*2+r_agree_percent-r_disagree_percent*1-r_s_disagree_percent*2)

teacher_tcr_quality_<-teacher_tcr_quality_ %>% mutate(c_s_disagree_percent = c_s_disagree/(c_s_disagree+c_s_agree+c_agree+c_disagree))%>%
  mutate(c_s_agree_percent = c_s_agree/(c_s_disagree+c_s_agree+c_agree+c_disagree))%>%
  mutate(c_agree_percent = c_agree/(c_s_disagree+c_s_agree+c_agree+c_disagree))%>%
  mutate(c_disagree_percent =  c_disagree/(c_s_disagree+c_s_agree+c_agree+c_disagree))%>%
  mutate(collaborate_score = c_s_agree_percent*2+c_agree_percent-c_disagree_percent*1-c_s_disagree_percent*2)

teacher_tcr_quality_<-teacher_tcr_quality_ %>% mutate(t_s_disagree_percent = t_s_disagree/(t_s_disagree+t_s_agree+t_agree+t_disagree))%>%
  mutate(t_s_agree_percent = t_s_agree/(t_s_disagree+t_s_agree+t_agree+t_disagree))%>%
  mutate(t_agree_percent = t_agree/(t_s_disagree+t_s_agree+t_agree+t_disagree))%>%
  mutate(t_disagree_percent =  t_disagree/(t_s_disagree+t_s_agree+t_agree+t_disagree))%>%
  mutate(trust_score = t_s_agree_percent*2+t_agree_percent-t_disagree_percent*1-t_s_disagree_percent*2)
                               
```

```{r}
library(GGally)
data <- teacher_tcr_quality_ %>% select(respect_score,trust_score,collaborate_score,t_score,p_score,st_score)
 
ggpairs(data, title="") 
```

